\begin{thebibliography}{55}

\bibitem{tigani2025cpu}
Tigani, S., et al.: CPU-Only Self Enhancing Authoring Copilot Design-Based Markov Decision Processes Orchestration and Qwen 3 Local LLM. Economies \textbf{13}(11), 520 (2025)

\bibitem{hao2024hybrid}
Hao, Z., et al.: Hybrid SLM and LLM for Edge-Cloud Collaborative Inference. In: EdgeFM '24. ACM (2024)

\bibitem{xie2025fusing}
Xie, L., et al.: Fusing Domain Knowledge with a Fine-Tuned Large Language Model for Enhanced Molecular Property Prediction. J. Chem. Inf. Model. \textbf{21}(14) (2025)

\bibitem{alabbasi2024teleoracle}
Alabbasi, N., et al.: TeleOracle: Fine-Tuned Retrieval-Augmented Generation with Long-Context Support for Networks. arXiv:2411.02617 (2024)

\bibitem{cao2025enersafe}
Cao, Q., et al.: Toward Energy-Safe Industrial Monitoring: A Hybrid LLM Framework for Video Captioning. Appl. Sci. \textbf{15}, 12848 (2025)

\bibitem{lee2024orchestrallm}
Lee, C.-H., et al.: OrchestraLLM: Efficient Orchestration of Language Models for Dialogue State Tracking. arXiv:2311.09758 (2024)

\bibitem{han2025commentagent}
Han, X., et al.: CommentAgent: a LLM-powered agent framework for automated comment generation and opinion understanding. J. Supercomput. \textbf{81}(15) (2025)

\bibitem{aydin2025integrated}
Aydin, S.K., et al.: An Integrated AI Framework for Personalized Nutrition Using ML and NLP for Dietary Recommendations. Appl. Sci. \textbf{15}(17) (2025)

\bibitem{demir2025dpatransllm}
Demir, E., Bilgin, M.: DPATransLLM: Detection of Pronominal Anaphora in Turkish Sentences Using Transformer-Based LLMs. Appl. Sci. \textbf{15}(23) (2025)

\bibitem{ji2025raprag}
Ji, X., et al.: RAP-RAG: A Retrieval-Augmented Generation Framework with Adaptive Retrieval Task Planning. Electronics \textbf{14}(21) (2025)

\bibitem{pacheco2025flight}
Pacheco De Almeida Prado, J., et al.: Enhancing Flight Deck Decision Support with Distributed GenAI: A Multi-Agent Approach. IEEE Aero. (2025)

\bibitem{dorfner2024comparing}
Dorfner, F.J., et al.: Comparing Commercial and Open-Source LLMs for Labeling Chest Radiograph Reports. Radiology \textbf{313}(1) (2024)

\bibitem{zhu2024ofslms}
Zhu, J., et al.: OFSLMs: Offline Fine-Tuned SLMs based on Hybrid Synthetic Knowledge for Robot Introspective Decision-making. IEEE ROBIO (2024)

\bibitem{jeong2023testtime}
Jeong, S., et al.: Test-Time Self-Adaptive Small Language Models for Question Answering. EMNLP (2023)

\bibitem{oh2025uncertainty}
Oh, S., et al.: Uncertainty-Aware Hybrid Inference with On-Device Small and Remote Large Language Models. arXiv:2412.12687 (2025)

\bibitem{amarasinghe2025fipo}
Amarasinghe, P.T., et al.: Feedback-integrated Prompt Optimiser for Problem Formulation. Sci. Rep. \textbf{15}, 43543 (2025)

\bibitem{chatzistefanidis2025survey}
Chatzistefanidis, G., et al.: Symbiotic Large and Small Language Models: A Survey. arXiv:2501.00000 (2025)

\bibitem{han2025chest}
Han, J., et al.: Self-Reflective Chest X-Ray Report Generation. J. Med. Syst. \textbf{49}, 190 (2025)

\bibitem{pietrzak2025evaluation}
Pietrzak, Z., et al.: Holistic Evaluation of TinyLlama-Generated Synthetic Cyber Threat Intelligence. Electronics \textbf{14}, 4971 (2025)

\bibitem{weiss2025investigating}
Weiss, Y., Buttery, P., Africa, D.D., Diehl Martinez, R.: Investigating ReLoRA: Effects on the Learning Dynamics of Small Language Models. arXiv preprint arXiv:2509.12960 (2025)

\bibitem{gao2025uncertainty}
Gao, Y., Myers, S., Chen, S., Dligach, D., Miller, T., Bitterman, D.S., et al.: Uncertainty estimation in diagnosis generation from large language models: next-word probability is not pre-test probability. JAMIA Open \textbf{8}(1), ooae154 (2025)

\bibitem{xiong2025resiliomate}
Xiong, Y., Huang, M., Liang, X., Tao, M.: ResilioMate: A Resilient Multi-Agent Task Executing Framework for Enhancing Small Language Models. IEEE Access \textbf{13}, 86892--86911 (2025)

\bibitem{ahmed2025arabic}
Ahmed, M., Arefeen, M.A., Zobaed, S.M., Rouf, M.T., Saha, S., Rahman, M.S.I.: Adapting Large Language Models for Arabic: Comparative Evaluation, Fine-Tuning, and Ethical Deployment. IEEE Access \textbf{13}, 12902--12928 (2025)

\bibitem{rahman2024prompt}
Rahman, M.S.I., Arefeen, M.A., Rouf, M.T., Ahmed, M., Zobaed, S.M., Saha, S., Samanta, S.: Prompt Design for Medical Question Answering with Large Language Models. IEEE Access \textbf{12}, 168239--168266 (2024)

\bibitem{han2025weighted}
Han, X., Han, C., Chen, Y., Wei, J.: A Weighted Voting Approach for Traditional Chinese Medicine Formula Classification Using Large Language Models: Algorithm Development and Validation Study. JMIR Med. Inform. \textbf{13}, e60787 (2025)

\bibitem{dodson2026explainable}
Dodson, R.J.B., Dodson, C.R.S., Dodson, P.S., et al.: Explainable machine learning-based prediction of psoriatic arthritis flares using heterogenous real-world data for personalised patient care. Rheumatology \textbf{65}(2), 528--537 (2026)

\bibitem{liu2025vte}
Liu, X., Myers, S., Bitterman, D.S., Dligach, D., Miller, T., Afshar, M., Gao, Y.: Improving VTE Identification through Language Models from Radiology Reports: A Comparative Study of Mamba, Phi-3 Mini, and BERT. JAMIA Open \textbf{8}(1), ooae155 (2025)

\bibitem{zeng2026multiagent}
Zeng, J., Liao, J., Sun, S., Zhang, G., Xu, C., Liu, H., Li, Y.: Multi-Agent Collaborative Reasoning via Cloud-Edge Framework. IEEE Network (2026). DOI: 10.1109/MNET.2026.3651036

\bibitem{krishna2024compos}
Krishna, S.V., Saini, A.N.: Compos Mentis at SemEval-2024 Task 6: A Multi-Faceted Role-based Large Language Model Ensemble to Detect Hallucination. In: Proc. SemEval-2024, pp. 930--944. ACL (2024) 

\bibitem{chen2025integrating}
Chen, Y., Ma, S., Wang, S., Shi, J.: Integrating Reinforcement Learning and LLM with Self-Optimization Network System. IEEE Commun. Lett. \textbf{29}(1), 228--232 (2025)

\bibitem{alabbasi2024leveraging}
Alabbasi, N., Erak, O., Alhussein, O., Lotfi, I., Muhaidat, S., Debbah, M.: Leveraging Fine-Tuned Retrieval-Augmented Generation with Long-Context Support: For 3GPP Standards. arXiv preprint arXiv:2411.02617 (2024)

\bibitem{miller2024towards}
Miller, K., Ghosh, S., Neumann, F.: Towards Optimizing a Retrieval Augmented Generation using Large Language Model on Academic Data. Bachelor Thesis, University of Adelaide (2024)

\bibitem{alabbasi2024rethinking}
Alabbasi, N., Alhussein, O., Muhaidat, S., Debbah, M.: Do you actually need an LLM? Rethinking language models for customer reviews analysis. arXiv preprint arXiv:2411.02555 (2024)

\bibitem{solat2025federated}
Solat, F., Lee, J., Seif, M., Niyato, D., Poor, H.V.: Federated Learning-Enabled Hybrid Language Models for Communication-Efficient Token Transmission. IEEE Internet Things J. \textbf{12}(24), 53574--53587 (2025)

\bibitem{wilhelm2025beyond}
Wilhelm, P., Wittkopp, T., Kao, O.: Beyond Test-Time Compute Strategies: Advocating Energy-per-Token in LLM Inference. In: Proc. 5th Workshop on Machine Learning and Systems (EuroMLSys '25), pp. 1--7. ACM (2025)

\bibitem{lee2025democratizing}
Lee, C., Kumar, S., Vogt, K.A., Munshi, M., Tallapudi, P., Vogt, A., Awad, H., Khan, W.: Democratizing cost-effective, agentic artificial intelligence to multilingual medical summarization through knowledge distillation. Sci. Rep. \textbf{15}, 27619 (2025)

\bibitem{jin2025hlmea}
Jin, X., Wang, Z., Chen, J., Yang, L., Oh, B., Hwang, S., Li, J.: HLMEA: Unsupervised Entity Alignment Based on Hybrid Language Models. In: Proc. 39th AAAI Conf. on Artificial Intelligence (AAAI-25). AAAI (2025)

\bibitem{huynh2025collaborating}
Huynh, T., Nguyen, D.: Collaborating Agents with Large Language Models for Question-Answering Tasks. In: Proc. 5th IEEE Int. Conf. on Software Engineering and Artificial Intelligence (SEAI), pp. 1--7. IEEE (2025)

\bibitem{aldaoud2024enhancing}
Al Daoud, E., Al Daoud, L., Asassfeh, M., Al-Shaikh, A., Al-Sherideh, A.S., Afaneh, S.: Enhancing Cybersecurity with Transformers: Preventing Phishing Emails and Social Media Scams. In: Proc. IEEE Conf. on Dependable and Secure Computing (DSC), pp. 1--8. IEEE (2024)

\bibitem{ying2025beyond}
Ying, S., Li, Z., Yu, M.: Beyond Words: Evaluating Large Language Models in Transportation Planning. arXiv preprint arXiv:2408.01633 (2024)

\bibitem{pintelas2025textnex}
Pintelas, E., Koursaris, A., Livieris, I.E., Tampakas, V.: TextNeX: Text Network of eXperts for Robust Text Classification—Case Study on Machine-Generated-Text Detection. Mathematics \textbf{13}(10), 1555 (2025)

\bibitem{estebanromero2025synthesizing}
Esteban-Romero, S., Martín-Fernández, I., Gil-Martín, M., Fernández-Martínez, F.: Synthesizing Olfactory Understanding: Multimodal Language Models for Image-Text Smell Matching. Symmetry \textbf{17}(8), 1021 (2025)

\bibitem{shivarpatna2025empirical}
Shivarpatna Venkatesh, A.P., Sunil, R., Sabu, S., Reis, M.S., Bodden, E., Amir, M.: An Empirical Study of Large Language Models for Type and Call Graph Analysis in Python and JavaScript. arXiv preprint arXiv:2410.00603 (2025)

\bibitem{zhu2024distilling}
Zhu, X., Li, J., Liu, Y., Ma, C., Wang, W.: Distilling Mathematical Reasoning Capabilities into Small Language Models. arXiv preprint arXiv:2401.11864 (2024)

\bibitem{gichamba2024colbert}
Gichamba, A., Idris, T.K., Ebiyau, B., Nyberg, E., Mitamura, T.: ColBERT Retrieval and Ensemble Response Scoring for Language Model Question Answering. arXiv preprint arXiv:2408.10808 (2024)

\bibitem{she2025token}
She, J., Zheng, W., Liu, Z., Wang, H., Xing, E., Yao, H., Ho, Q.: Token Level Routing Inference System for Edge Devices. arXiv preprint arXiv:2504.07878 (2025)

\bibitem{cielen2026exploring}
Cielen, D., De Bock, K.W., Florès, L.: Exploring Zero-Shot SLM ensembles as an alternative to LLMs for sentiment analysis. Information Fusion \textbf{126}, 103666 (2026)

\bibitem{bao2025dynamic}
Bao, R., Xue, N., Sun, Y., Chen, Z.: Dynamic Quality-Latency Aware Routing for LLM Inference in Wireless Edge-Device Networks. arXiv preprint arXiv:2508.11291 (2025)

\bibitem{chen2025edge}
Chen, H., Deng, W., Yang, S., Xu, J., Jiang, Z., Ngai, E.C.H., Liu, J., Liu, X.: Toward Edge General Intelligence via Large Language Models: Opportunities and Challenges. arXiv preprint arXiv:2410.18125 (2025)

\bibitem{li2025item}
Li, M., Jiao, H., Zhou, T., Zhang, N., Peters, S., Lissitz, R.W.: Item Difficulty Modeling Using Fine-tuned Small and Large Language Models. In: Proc. 19th Workshop on Innovative Use of NLP for Building Educational Applications (BEA 2024), pp. 1--10 (2025)

\bibitem{mehandru2025bioagents}
Mehandru, N., Hall, A.K., Melnichenko, O., Dubinina, Y., Tsirulnikov, D., Bamman, D., Alaa, A., Saponas, S., Malladi, V.S.: BioAgents: Bridging the gap in bioinformatics analysis with multi-agent systems. Sci. Rep. \textbf{15}, 39036 (2025)

\bibitem{shao2025dot}
Shao, C., Hu, X., Lin, Y., Xu, F.: Division-of-Thoughts: Harnessing Hybrid Language Model Synergy for Efficient On-Device Agents. In: Proc. of the ACM Web Conference 2025 (WWW '25), pp. 1822--1833. ACM (2025)

\bibitem{li2024mixed}
Li, C., Chen, Q., Li, L., Wang, C., Li, Y., Chen, Z., Zhang, Y.: Mixed Distillation Helps Smaller Language Model Better Reasoning. arXiv preprint arXiv:2312.10730 (2024)

\bibitem{abbas2025cognitive}
Abbas, N., Atwell, E.: Cognitive Computing with Large Language Models for Student Assessment Feedback. Big Data Cogn. Comput. \textbf{9}(5), 112 (2025)

\end{thebibliography}